Summer 2025 ToDo

### 2025-07-25 Relations/Paper/Well-foundedness.tex
wf diagram update
Well-founded work in progress update

\apcomment{Well-foundedness or wellfoundedness?}

An abstract reduction $\to_R$ is strongly normalizing
if and only if the converse relation is well-founded.
In this section, we will compare several definitions of well-foundedness.

\subsection{New version: Synopsis and Outline}

Classically, well-foundedness can be defined in several equivalent but distinct ways:
by induction, by absence of decreasing sequences, and by the fact that every
subset has a minimal element.  Constructively, these are no longer equivalent.
Moreover, even individual classical definitions can be given constructive
interpretations in varying degrees of logical strength.

@@

\subsection{The main definitions}

The various formulations of well-foundedness are based on the following notions.
\begin{definition}
  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
  \begin{enumerate}
    \item $P \subseteq A$ is \emph{inductive}
    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.

    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
  \end{enumerate}
\end{definition}

>>>>

% We use Well-founded not Wellfounded

An abstract reduction $\to_R$ is strongly normalizing
if and only if the converse relation is well-founded.
In this section, we will compare several definitions of well-foundedness, which depend on the following properties.
\begin{definition}
  Let $R \subseteq A \times A$.  We write $Rxy$ when $(x,y) \in R$.
  \begin{enumerate}
    \item $P \subseteq A$ is \emph{inductive}
    if, for each $x \in A$, $(\forall y. Ryx \to y \in P)$ implies $x \in P$.

    \item $s : \nat \to A$ is \emph{$R$-decreasing} if for all $k$, $(s(k+1),s(k)) \in R$.
  \end{enumerate}
\end{definition}
\apcomment{Add the definitions of well-foundedness here and then continue with the text as below.}
\subsection{New version: Synopsis and Outline}

Classically, the above notions of well-foundedness are all equivalent.  Constructively, only the first two are equivalent; the remaining definitions are not. Moreover, even individual classical definitions can be given constructive
interpretations in varying degrees of logical strength.

@@
